### 2024-06-01 getting-started.qmd
20240601 - names

```{r}
players <- data.frame(
  ID = 1:10,
  name = c(
    "Ken Cussion",
    "Ben Sacked",
    "Ron Ingback",
    "Lionel Scrimmage",
    "Drew Blood",
    "Hugo Long",
    "Chase Emdown",
    "Justin Time",
    "Name9",
    "Name10"),
  position = c("QB","QB","RB","RB","WR","WR","WR","WR","TE","TE"),
  age = c(40, 30, 20, 18, 23, 27, 32, 26, 23, NA)
  )

>>>>

```{r}
players <- data.frame(
  ID = 1:10,
  name = c(
    "Ken Cussion",
    "Ben Sacked",
    "Ron Ingback",
    "Rhonda Ball",
    "Hugo Long",
    "Lionel Scrimmage",
    "Drew Blood",
    "Chase Emdown",
    "Justin Time",
    "Name10"),
  position = c("QB","QB","RB","RB","WR","WR","WR","WR","TE","TE"),
  age = c(40, 30, 20, 18, 23, 27, 32, 26, 23, NA)
  )
